Master Thesis

### 2013-07-02 abstract.tex
Typo in abstract

\begin{abstract}
We present work whose ultimate goal is the creation of wide-coverage
abstract categorial grammars (ACGs) that could be used to automatically
build discourse-level representations. In our work, we advance towards
that goal by laying down the foundations necessary for building
wide-coverage ACGs.

>>>>

\begin{abstract}
We present work whose ultimate goal is the creation of a wide-coverage
abstract categorial grammar (ACG) that could be used to automatically
build discourse-level representations. In our work, we advance towards
that goal by laying down the foundations necessary for building
wide-coverage ACGs.
